---
title: "Lab 00 - Hello IDS!"
author: "Athos Rocha"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Athos Rocha", "Anniruddh Viyer", "Louis Newton", 
           "Ethan Wood", "Jacob Cullen", "Lucas Smith"),
  github_username = c("athos-roch", "aniruddhviyer", 
                      "LouisWeil", "EJamesW05", "s2543550", "ls657"), 
  colour = c("green", "navyblue", "turquoise", "navyblue", 
             "blue", "hotpink"),
  hobby = c("Karting", "Hiking", "Triathalon", 
            "Reading Novels", "Football", "Going Out"),
  favourite_number = c(5, 4, 7, 10, 8, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

This graph shows the team members favourite number and favourite color against their GitHub username.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "Facts about Team-members")
```

This graph shows the team members favourite number and favourite color against their GitHub username.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```


